### 2025-03-05 src/paper.tex

\input{include/header}

\begin{document}

\section{Введение}

\input{introduction.tex}

\section{Постановка задачи}

\input{problem_setup.tex}

\section{Определение сложности задачи} % Дополнить

\label{seg:complexity}

\input{complexity.tex}

\section{Подход Чайтина}

\input{chatin.tex}

\section{Подход Бриггса}

\input{brigs.tex}

\section{Подход Полетто}

\input{poletto.tex}

\bibliography{include/my.bib}{}

\bibliographystyle{gost2008s}

\end{document}